%-------------------------
% Resume in Latex
% Author : Gennadii Chursov
% Based off of: https://github.com/sb2nov/resume and https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[UKenglish]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

\newcommand{\experienceItem}[5]{
  \item 
  \begin{minipage}[t]{0.75\textwidth}
    \textbf{#1} $|$ #2 #5
  \end{minipage}
  \begin{minipage}[t]{0.2\textwidth}
    \begin{flushright}
      % \textbf{#3}\\
      #3\\
      #4
    \end{flushright}
  \end{minipage}
}

\newcommand{\educationItem}[4]{
  \vspace{-2pt}
  \item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{#2} \\
    \small#3 & \small#4
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}, itemsep=7pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[noitemsep,topsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Rintaro Kawagishi} \\ \vspace{1pt}
    +44 7876 085448 $|$ 
		\href{mailto:rintaro.kawagishi@gmail.com}{\underline{rintaro.kawagishi@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/rintaro-kawagishi}{\underline{https://www.linkedin.com/in/rintaro-kawagishi}}
\end{center}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, Kotlin, Swift, C++, C, Python, SQL, HTML, CSS, PHP} \\
     \textbf{Frameworks}{: Next.js, React, React Native, Kotlin Multiplatform, Node.js, FastAPI, Expo, Playwright} \\
     \textbf{Developer Tools}{: AWS, Docker, Supabase, PostgreSQL, Git, Kibana, Terraform}
    }}
 \end{itemize}

\section{Experience}
  \resumeSubHeadingListStart
    \experienceItem
      {Software Developer}
      {Softwire}
			{Sep.\ 2022 -- Present}
      {London, UK}
      {
        \resumeItemListStart
          \resumeItem{Produced an online Corporate Power Purchase Agreements evaluation tool for   a consultancy firm using Next.js and FastAPI with Python interacting with various AWS services.}
          \resumeItem{Directed a team of six developers in revamping a London-based food bank website to be used by the food bank volunteers; Implemented local database configurations and CI/CD pipelines to automate database migrations to two deployed environments, cutting deployment time by 50\%; Configured AWS CloudWatch using Infrastructure as Code to log website events and monitor website health; Facilitated meetings within the team and with the project stakeholders to scope pieces of work.}
          \resumeItem{Line-managed five junior developers and led their initial training process.}
          \resumeItem{Took ownership of the pro bono mobile app development for a charity organisation focusing on Black history education for children; Identified tasks required for the first release whilst managing client expectations as the project is not billable.}
          \resumeItem{Contributed to the maintenance of LNER’s website and award-winning app; Spearheaded the development of a new ticket type which has been rolled out to production, for which I have been nominated for an Individual Outcome Award.}
          \resumeItem{Received an Individual Outcome Award on my first project for a financial asset management firm, where I developed a template system for Alteryx which sped up the development process by 20 times.}
          \resumeItem{Mentored three GCSE students during their work experience, building a rudimentary Tetris web application.}
        \resumeItemListEnd
      }

    \experienceItem
      {Software Developer Intern}
      {Softwire}
      {Jun.\ 2021 -- Aug.\ 2021}
      {London, UK}
      {
        \resumeItemListStart
          \resumeItem{Played a pivotal role in the development of the Black history app on a team of six, developing the app from the ground up and subsequently taking ownership of the project after I joined the company as an employee.}
        \resumeItemListEnd
      }

    \experienceItem
      {Consultancy Intern}
      {Automation Consultants}
			{Jun. 2020 -- Sep. 2020}
      {Reading, UK}
      {
        \resumeItemListStart
          \resumeItem{Modularised essential components of the company’s WordPress website using HTML, CSS and PHP,
          speeding the content editing process up by 10 times.}
          \resumeItem{Developed a website performance assessment script in Python to help them improve their SEO.}
        \resumeItemListEnd
      }

    \experienceItem
      {Engineering Intern}
      {Mitsubishi Electric R\&D Centre Europe}
			{Jun.\ 2019 -- Jul.\ 2019}
      {Livingston, UK}
      {
        \resumeItemListStart
          \resumeItem{Designed 3D models of the mechanical structure of a future railway passenger carriage using Solidworks.}
          \resumeItem{Developed a C program to analyse the 3D data sets of temperature and air velocity simulation results to compute passenger comfort and visualised the output using Paraview.}
        \resumeItemListEnd
      }
  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \experienceItem
      {University of Cambridge}
      {BA (Hons) \& Master of Engineering with a Merit}
      {2018 -- 2022}
      {Cambridge, UK}
      {
        \resumeItemListStart
          \resumeItem{Specialised in Information and Aerospace Engineering, including modules in Probabilistic Machine Learning, Deep Learning, Computer Vision, Information Theory and Fluid Mechanics.}
        \resumeItemListEnd
      }
    
  \resumeSubHeadingListEnd

  % \section{Projects}
  % \resumeSubHeadingListStart
  %   \experienceItem
  %     {Pilot Community Website}
  %     {Next.js, TypeScript, AWS, Supabase, Docker}
  %     {Jan.\ 2024 -- Present}
  %     {}
  %     {
  %       \resumeItemListStart
  %         \resumeItem{Developing a full-stack web application to connect pilots across the country}
  %         \resumeItem{Created a password authentication flow using AWS Cognito}
  %         \resumeItem{Implemented a JWT authentication token in the backend to manage sessions}
  %       \resumeItemListEnd
  %     } 
  % \resumeSubHeadingListEnd

% \section{Certifications}
%   \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Cloud Digital Leader - Google Cloud} \\
%      \textit{Issued Sep 2022 - Expires Sep 2025} \\
%     }}
%  \end{itemize}

\end{document}
